---
title: "GSS challange More Data"
author: "America Olivo!"
date: "10/6/2022"
output: html_document
---







```{r include=FALSE,echo=FALSE}
source(file="fisherXY.R")
require(tidyverse)
require(tigerstats)
require(knitr)
require(foreign)
GSS <-read.dta(file="GSS2016.dta")
GSS <- droplevels(GSS)
mydata <- select(GSS,race,cappun)
mydata <- na.omit(mydata)
```

# Introduction

<!--In this section you explain what you are trying to show.  Where did the data come from?  What is the research or other question you are trying to answer?.  If you skimp in this section expect to be marked down in your grade. Paint a picture of the project a couple of paragraphs is expected!-->

Is attitude toward capitol punishment (cappun) independent of race (race)?
If not, then whose view differs from whom??

```{r eval=FALSE}
mydata<-mydata %>% 
mutate(across(where(is.character), as.factor))
```
# Methods
<!--Decide on your methods:  use "variable analysis" or other appropriate descriptors.  Make sure to choose at least one graphical method and at least one numerical method. Discuss what data manipulations may be needed for example subsetting or other binning procedures and what sort of graphical displays and inferential tools will be used!-->

The methods that will be used for this problem is a numerical graphical , and inferential tests from the cat cat helper file to figure out if capital punishment depends on race. 

# Results

<!--Divide this section into two sub-sections:  One for your descriptive  results and one for your inferential results.!-->
## Descriptive Results

### Graphical Descriptive Results

<!--Graphical results here.  Make sure to show your code.  Provide appropriate labels for axes, giving units if possible, and provide a good title for the graph, too.  Use the graphical results to describe the patterns if any that exist in the data as focused toward the research question. Bottom line is to explain the features of the graph that are relevant to conforming or departing to what is expected by your null hypothesis !-->

```{r}
barchartGC(~race + cappun, data=mydata)
barchartGC(~race + cappun,data=mydata, type ="percent")
```

There is a very huge difference between the two. Over 60% of white people are for capital punishment and about 55% of black people are oppose of capital punishment. 35% of white people are oppose to it and 45% of black people who are for it. The other races had a 55% of people who are in favor and about 45% who are oppose of it. The plot shows that the white people are for capital punishment then other races, then lastly black people have the most people who oppose capital punishment. The white people are for it 2 to 1 and black people are oppose of it 5 to 4. 

## Now with The Most data (fewer variables gives more data points)



### Numerical Descriptive Results

<!--Numerical results go here. Use the numerical results to describe the patterns if any that exist in the data as focused toward the research question!-->

```{r}
table1 <- xtabs(~race + cappun, data=mydata)
rowPerc(table1)
colPerc(table1)
```

There is 65% white people who favor capital punishment and 34% who oppose of it, there are 42% of black people who favor it and 57% who oppose it, lastly other races 55% favor it and 44% oppose of it. the biggest difference is between the white people and the black people.

## Now with More data



## Inferential Results

<!--State hypothesis clearly.  Make sure your discussion of the inferential test covers all the aspects that the test output produces, such as test statistic, p-value etc.  Make a decision about the null hypothesis, explain the assumptions on which the selected test/procedure was based, and why the chosen procedure satisfys the assumptions and is appropriate to answer the research question!-->

```{r}
chisq.test(table1)
chisqtestGC(table1)
fisher.test(table1)
```




```{r}
fisherXY(mydata$race,mydata$cappun)
```
 
  Each group has a different opinion and not one race has a common opinion. 


## More data version
This data had more participants which helped get the closest number to get  more accurate data. 

# Discussion and Conclusion

<!--Discussion and conclusion here.  If you found a relationship be sure to consider whether the relationship occurs because one of the variavbles causes the other, or whether they perhasps are related for some other reason.  Watch the chapter 6 videos from the GeorgeTown videos collection.!-->

In the master branch we had a larger number of participants who were surveyed which helps the odds ratio converge to a normal distribution. It also shows in the graphical results that white people are more likely to support capital punishment and black people oppose of it because of their race. Race is a factor and is a independent variable. 

